\documentclass{llncs}
\usepackage[utf8]{inputenc}

\begin{document}

% Please remember the 2-page maximum size for each workshop

\section*{Asynchronous Many-Task systems for Exascale (AMTE)}

\subsection*{Workshop Description}
The workshop, Asynchronous Many-Task Systems for Exascale (AMTE) 2024, was held on August 26th in conjunction with the 30th International European Conference on Parallel and Distributed Computing (Euro-Par) as an in-person event in Madrid, Spain. The workshop explored the advantages of task-based programming on modern and future high-performance systems. It gathered developers, users, and proponents of these models and systems to share experiences, discuss how they meet the challenges posed by Exascale system architectures, and explore opportunities for increased performance, robustness, and full-system utilization.

The workshop was organized by Patrick Diehl, Steven R. Brandt, Zahra Khatami, and Parsa Amini. The keynote was given by Joel Falcou (University Paris-Sud, Interdisciplinary Laboratory of Numerical
Sciences (LISN)), and the invited talk was given by Mehdi Goli (Codeplay). 

This volume of LNCS compromises selected contributions of attendees from this event. The contributed papers range from optimization of asynchronous many-task runtime systems to applications. This workshop has shown that AMTs are widely used in academia, industry, and national laboratories, and researchers are working to address some challenges posed by Excascale system architectures.


\subsection*{Steering Committee}
%Please introduce one name and affiliation per line as below.
\begin{tabular}{@{}p{5cm}@{}p{7.2cm}@{}}
Parsa Amini & Halpern-Wight Inc., USA\\
Steven R. Brandt & Louisiana State University, USA\\
Patrick Diehl & Los Alamos National Laboratory, USA\\
Zahra Khatami & NVIDIA, USA\\
\end{tabular}


%\subsection*{Program Chair}
%In case of more than one char, please introduce one name and affiliation per line as below.
%\begin{tabular}{@{}p{5cm}@{}p{7.2cm}@{}}
%Loris Marchal & CNRS \& University of Lyon, France
%\end{tabular}

\subsection*{Program Committee}
%Please introduce one name and affiliation per line as below.
\begin{tabular}{@{}p{5cm}@{}p{7.2cm}@{}}
    Markus Rampp & Max Planck Computing and Data Facility, Germany \\
     Jonas Posner & University of Kassel, Germany \\
     Hartmut Kaiser & Louisiana State University, USA \\
     Sumathi Lakshmiranganatha & Los Alamos National Laboratory, USA \\
     Brad Richardson & Sourcery Institute, USA \\
     Chris Taylor &  Tatical Computing Lab, USA \\
      Marc-André Vef & Johannes Gutenberg-University Mainz, Germany \\
     Javier Fernandez Muñoz & University Carlos III of Madrid, Spain \\
     Pierre-Francois Dutot & Université Grenoble Alpes, France 
\end{tabular}
\raggedbottom\\
\hspace{1cm}\\
LA-UR-
\end{document}